Case for Support

### 2021-11-17 application/caseForSupport.tex
Merging references conflict

    \item[Understanding the brain and behaviour] Systems neuroscientists aim to
        uncover how adaptive behaviour arises from computation in neural
        circuits in different brain regions. Extending the Bonsai ecosystem
        will facilitate new types of experiment that causally connect neural
        circuits with elemental behavioural processes. Long-term, this research
        will help identify missing links between circuit dysfunction and
        behavioural deficits in neurological or mental health disorders, and
        will support the development of new neural circuit biomarkers
        and therapies. The Bonsai ecosystem will also enable  experimental
        testing of emerging theories of brain function and learning, and thus
        contribute to the neuro-inspired machine learning algorithms that fuel
        intelligent technologies, increasingly important in our society.  The
        enhanced Bonsai platform will also support purely behavioural
        experiments, which track animals' posture, body parts or location in real-time, to investigate impacts of environmental variables
        or captivity on behaviour - crucial for
        animal welfare.

@@

    \item[Improve efficiency of research] Most neuroscience laboratories
        worldwide develop custom, unique solutions to their experimental
        control and analysis needs. Some laboratories also lack the technical
        know-how to either develop their own software for experimental hardware
        control or write software for state-of-the-art analysis of rich
        neural and behavioural data, increasingly reliant on latest machine
        learning algorithms. The proposed upgrading of the open-source and
        community-empowered Bonsai ecosystem with a toolbox of online and
        offline analytical tools, which can dovetail with closed-loop
        experimental requirements, will (i) allow the deployment of such tools
        into laboratories that lack the necessary expertise, (ii) reduce the need to
        reinvent the same tools in multiple labs (cost/time efficiency) and
        (iii) concomitantly streamline and standardise the experimental data
        processing streams in systems neuroscience.

>>>>

    \item[Understanding the brain and behaviour] Systems neuroscientists aim to
        uncover how adaptive behaviour arises from computation in neural
        circuits in different brain regions. Extending the Bonsai ecosystem
        will facilitate new types of experiment that causally connect neural
        circuits with elemental behavioural processes. Long-term, this research
        will help identify missing links between circuit dysfunction and
        behavioural deficits in neurological or mental health disorders, and
        will support the development of new neural circuit biomarkers
        and therapies. The Bonsai ecosystem will also enable  experimental
        testing of emerging theories of brain function and learning, and thus
        contribute to the neuro-inspired ML algorithms that fuel
        intelligent technologies, increasingly important in our society.  The
        enhanced Bonsai platform will also support purely behavioural
        experiments, which track animals' posture, body parts or location in real-time, to investigate impacts of environmental variables
        or captivity on behaviour - crucial for
        animal welfare.

@@

    \item[Improve efficiency of research] Most neuroscience laboratories
        worldwide develop custom, unique solutions to their experimental
        control and analysis needs. Some laboratories also lack the technical
        know-how to either develop their own software for experimental hardware
        control or write software for state-of-the-art analysis of rich
        neural and behavioural data, increasingly reliant on the latest ML algorithms. The proposed upgrading of the open-source and
        community-empowered Bonsai ecosystem with a toolbox of online and
        offline analytical tools, which can dovetail with closed-loop
        experimental requirements, will (i) allow the deployment of such tools
        into laboratories that lack the necessary expertise, (ii) reduce the need to
        reinvent the same tools in multiple labs (cost/time efficiency) and
        (iii) concomitantly streamline and standardise the experimental data
        processing streams in systems neuroscience.
